---
title: "Homework 5"
author: "Murrel Pereira"
date: "11/10/2020"
output: github_document
---

```{r setup, include=FALSE}
library(tidyverse)

knitr::opts_chunk$set(
  fig.width=6,
  fig.asp=.6,
  out.width ="90%"
)

theme_set(theme_minimal() +theme(legend.position = "bottom"))

options(
  ggplot2.continuous.color = "viridis",
  ggplot2.continuous.fill = "viridis"
)

scale_colour_discrete = scale_color_viridis_d
scale_fill_discrete=scale_fill_viridis_d

```

## Problem 1

Read in the data.

```{r}
homicide_df =
  read_csv("homicide_data/homicide-data.csv") %>% 
  janitor::clean_names() %>% 
  mutate(
    resolved = case_when(
      disposition == "Closed without arrest" ~ "unsolved",
      disposition == "Open/No arrest"        ~ "unsolved",
      disposition == "Closed by arrest"      ~ "solved"
    ),
    city_state = str_c(city, state, sep = "_")
  ) %>% 
  select(city_state, resolved) %>% 
  filter(city_state != "Tulsa_AL") 
  
```

Look at this a bit

```{r}
aggregate_df =
homicide_df %>% 
  group_by(city_state) %>% 
  summarize(
    hom_total = n(),
    hom_unsolved = sum(resolved == "unsolved")
  ) %>% 
  arrange(hom_unsolved)
```

Can I do a prop test for a single city?

```{r}
prop.test(
  aggregate_df %>% filter(city_state == "Baltimore_MD") %>% pull(hom_unsolved),
  aggregate_df %>% filter(city_state == "Baltimore_MD") %>% pull(hom_total)
) %>% 
  broom::tidy()
```

Try to iterate....

```{r}
results_df =
aggregate_df %>% 
  mutate(
    prop_tests = map2(.x = hom_unsolved, .y = hom_total, ~prop.test(x = .x, n = .y)),
    tidy_tests = map(.x=prop_tests, ~broom::tidy(.x))
  ) %>% select(-prop_tests) %>% 
  unnest(tidy_tests) %>% 
  select(city_state, estimate, conf.low, conf.high) %>% 
  arrange(desc(estimate))
  
  
```

```{r}
results_df %>% 
  mutate(city_state = fct_reorder(city_state, estimate)) %>% 
  ggplot(aes(x = city_state, y = estimate)) +
  geom_point() +
  geom_errorbar(aes(ymin = conf.low, ymax = conf.high)) +
  theme(axis.text.x = element_text(angle = 90, vjust = 1, hjust = 1))
  
```

## Problem 2

Create tidy dataset
```{r}

path_df = 
tibble(
  path = list.files("lda_data")
) %>% 
  mutate(
    path = str_c("lda_data/",path),
    obs = map(path, read_csv),
    treatment = case_when(
      str_detect(path, "con") ~ "control",
      str_detect(path, "exp") ~ "experimental"
    ),
    subject = substr(path, start = 10, stop =15),
    subject = as.factor(subject),
    treatment = as.factor(treatment)
  ) %>% 
  unnest(obs) %>% 
  pivot_longer(week_1:week_8,
              names_to ="week",
              names_prefix = "week_",
              values_to = "observations")

```

Create spaghetti plot
```{r}
ggplot(path_df, aes(x = week, y = observations, group = subject, color = treatment)) + geom_point() + geom_line() + 
  labs(title = "Observations over time",x = "Week", y= "Observations"
  )
```

You can see that the observations for the control group do not change over the 8 week period but in contrast, the observations for the experimental treatment group increase over time.

## Problem 3

Create function
```{r}
sim_t_test = function(mu = 1) {
  
  sim_data = tibble(
    x = rnorm(30, mean = mu, sd = 5),
  )
  
  sim_data %>% 
    t.test(mu = 0, alpha = .05) %>% 
    broom::tidy() %>% 
    select(estimate, p.value) 

}
```

Iterate function and save results
```{r}
sim_results =
  tibble(true_mu = c(1,2,3,4,5,6)) %>% 
  mutate(
    output_lists = map(.x = true_mu, ~rerun(5000, sim_t_test(mu = .x))),
    t_test_dfs = map(output_lists, bind_rows)
  ) %>% 
  select(-output_lists) %>% 
  unnest(t_test_dfs) %>% 
  mutate(
    outcome = case_when(
      p.value <= 0.05 ~ "null rejected",
      p.value > 0.05  ~ "null not rejected"
    ),
    true_mu = as.factor(true_mu)
  )
```

```{r}
sim_results_summary = 
  sim_results %>% 
  group_by(true_mu, outcome) %>% 
  summarize(n = n(), proportion = n/5000)
```

```{r}
ggplot(sim_results, aes(y = p.value, color = true_mu)) + geom_boxplot() + geom_hline(yintercept = 0.05, linetype = "dashed")
```

####Power of the test 
```{r}
ggplot(sim_results_summary, aes(x = true_mu, y = proportion, color = outcome, group = outcome)) + geom_point() + geom_line()
```

You can see in the above graph that the null is more likely to be rejected the further true_mu is away from 0 and the null is less likely to be rejected the closer true_mu is to 0. 

```{r}

```

